---
title: "TV Shows and Movies"
author: "Claire Yoon (ndq7xj), Tina Lin (tyl7jhm), Katie Tsai (nmu3tr)"
date: "2023-02-08"
output: 
  html_document:
    toc_depth: 3
    toc: true
    toc_float: true
    theme: lumen
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Objectives:

1) Explore topics and data for term project

2) Practice Rmd skills

Task:

Submit an html rendering of an Rmd notebook that contains:

1) Group member names

2) Topic for term project

3) 3-4 possible questions you would like to answers about your topic

4) Possible data sources (with links) and possible variables within those data sources that can answer your questions. 

Grading: 20 points

10 points for topic & data source information

10 points for Rmd syntax and style


Let's start with how to format our font:

**bold** Make this line bold

**Make this bold**

Make this line a Header 4

#### Make this line a Header 4

Insert a link on this line  

[Google](google.com)

Make this line italics  

*Make this line italics* 

Write something with superscript  

e=mc^2^

Write a block quote here

>"Hello world" 

Create an unordered list with 2 sub-items  

* Item 1
* Item 2
  - sub-item 1
  - sub-item 2
  
----

Preview your work - how does it look?

----

Write a line in inline code  
`df <- read.csv(data.csv)`

---

Write the same line of code in a code chunk

```
df <- read.csv(data.csv)
```

-or-

```{r}
x <- 5
x
```

---

In another code chunk, write code that will produce an output, but have that output suppressed.

```{r, eval = FALSE}
x <- 5
x
```


---

Import tidyverse without warnings being displayed. 
```{r, message = FALSE}
library(tidyverse)
```

---

Create a table with your 2 favorite TV shows and what channel/streaming service they are on. Center the table and its contents

TV show        | channel
:-:            | :-:
Emily in Paris | Netflix
Big Little Lies| HBO

----

Display that data is an easy to read manner.  Remember these reports are often written for people who are not familiar with the data or processes.

Print the built-in R dataframe iris. Without changing any settings, what do you think of the output in the html render?

```{r}
#iris
iris
```

----

Install the package kableExtra

kableExtra Documentation:
https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html#Overview

Load the package into this notebook. 

```{r}
library(kableExtra)
```

Using the kableExtra package, print the iris dataset with styling and a scroll box

```{r}
iris %>%
  kbl() %>%
  kable_styling("hover") %>%
  scroll_box(width = "600px", height = "200px")
```

----

Another package to handle table in Rmarkdown (among others) is DT

----

Let's create a table of contents (toc) for easy navigation. We'll need  head back to the YAML for configuration. 

Documentation: https://bookdown.org/yihui/rmarkdown/html-document.html

Create a toc that floats, uses the color scheme lumen, and recognizes headers to level 3


Then:

# Type a header 1

## Type a header 2

### Type a header 3

Type a header 1

Type a header 2

Type a header 3

Then: preview your document

----

## TV Shows and Movies {.tabset}

### Netflix
```{r}

  
```

### Prime Video

```{r}

  
```

### Hulu 

```{r}

```

### Disney+ {.tabset}

```{r}

  
```


